\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2022-07-26 R/scatterblob.Rmd
Lowercase "websites" in "Academic Websites"  and extends it to Personal

---
title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
output: html_document
# output: pdf_document
---

>>>>

---
title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
output: 
  html_document
---
